Automatic detection of bad habits of programming in Scratch

### 2014-04-18 paperFIE_en.tex
Refine some expressions

\paragraph{}Regarding the object namig, it is curious that Scratch users name correctly, ie significantly, the variables used in their projects. In our opinion the reason to explain this paradox is because it is mandatory to assign a name to a variable the moment it is created, as the environment does not name it by default. However, when creating a new character a  \textit{SpriteX} name is assigned automatically. A change on this feature of the environment, obliguing users to name new objects, would eliminate this malpractice.
\paragraph{}Regarding the code repetition and low usage Scratch users make of creating their own blocks (the equivalent of defining methods or procedures in other languages), works as the one performed by Seiter and Foreman \cite {seiter2013modeling}, in which they show that abstraction and modularization capacities are concepts that seem to be developed from a certain age, may explain the low rates of use of this functionality, since a significant part of the Scratch community consists of children under 10 years old\footnote{http://scratch.mit.edu/statistics/\#age}. Future studies should further investigate to continue advancing in the definition of an appropriate framework for different ages, as well as to check whether users learning online and those who do it in a regulated environment show different use rates of this functionality.

>>>>

\paragraph{}Regarding the object namig, it is curious that Scratch users name correctly, ie significantly, the variables used in their projects. In our opinion the reason to explain this paradox is because it is mandatory to assign a name to a variable the moment it is created, as the environment does not name it by default. However, when creating a new character a  \textit{SpriteX} name is assigned automatically. In our views, a change on this feature of the environment, obliguing users to name new objects, might eliminate this malpractice.
\paragraph{}Regarding the code repetition and the low usage Scratch users make of the possibility of creating their own blocks (the equivalent of defining methods or procedures in other languages), works as the one performed by Seiter and Foreman \cite {seiter2013modeling}, in which they show that abstraction and modularization capacities are concepts that seem to be developed from a certain age, may explain the low rates of use of this functionality, since a significant part of the Scratch community consists of children under 10 years old\footnote{http://scratch.mit.edu/statistics/\#age}. Future studies should further investigate to continue advancing in the definition of an appropriate framework for different ages, as well as to check whether users learning online and those who do it in a regulated environment show different use rates of this functionality.
